An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-09-04 neurips-19/poly-embed.tex
Added todos for camera ready

\documentclass[12pt]{article}
\PassOptionsToPackage{numbers, compress, sort}{natbib}
\usepackage{neurips_2019}

@@

Throughout this section, consider the surrogate and discrete loss $L^k(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ given in Equation~\ref{eq:L-2-surrogate}.

@@

>>>>

\documentclass[12pt]{article}
\PassOptionsToPackage{numbers, compress, sort}{natbib}
\usepackage[final]{neurips_2019}

@@

Consider the surrogate and discrete loss $L^k(u)_y~=~\left(\frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+$ given in Equation~\ref{eq:L-2-surrogate}.

@@

\hrule
\bigskip
TODO for camera-ready (tagging the person who'll probably end up doing it)
\begin{enumerate}
	\item \jessie{Make poster and link to it online}
	\item All: Address todos in paper.
	\item OPTIONAL: Make/link to slides and/or on paper
	\item Reviewer 1
	\begin{enumerate}
		\item \jessie{Clarify terms like \emph{reports} and \emph{properties}.}
	\end{enumerate}
	\item Reviewer 2 (didn't change review)
	\begin{enumerate}
		\item Provide more intuition for definitions
	\end{enumerate}
	\item Reviewer 3 (didn't change review)
	\begin{enumerate}
		\item \raf{Add discussion on the computational complexity (or lack thereof) of constructing $L$ and $\psi$}
		\item \jessie{Make sure we have corrected top-$k$ proof.}
	\end{enumerate}
	\item Meta-Review: ``Inserting all the comments made to answers R2 and R3 is a must for the paper to be very good.''
\end{enumerate}
